---
title: "Fragment survival"
author: "Ewout Knoester"
date: "11/08/2022"
output: html_document
---

#TODO: Layout of Treatment x Genus graph & Add sample numbers
#TODO: Add model for Structure x Size
#TODO: Layout of death graphs (numbers, colours, legend)
#TODO: Decide whether to show Treatment in most graphs or Structure type (ie not show compound mix) and adjust graphs accordingly

```{r setup}
rm(list=ls()) # Clear workspace
knitr::opts_knit$set(root.dir = '/tmp') #Set directory at current directory for all subsequent chunks

library(plyr) # Join data frames (vlookup)
library(readxl)
library(betareg) # Beta regression
library(writexl) # Export Excel
library(data.table)
library(stringr) # Select text from string
library(nlme) # GLS
library(lme4) # Gamma
library(DHARMa) # glm model validation
library(panelr) # Convert data from wide to long
library(tidyverse) # Data manipulation and plotting
library(ggthemes) # Pretty plots
library(emmeans) # Pairwise comparisons
library(multcompView) # Significance letters to plots
library(NCmisc) # Check packages used

# Function to facilitate averaging data frame
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      n  = length(x[[col]]),
      sd = sd(x[[col]], na.rm=TRUE),
      sum  = sum(x[[col]]),
      se = sd(x[[col]], na.rm=TRUE)/sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
 return(data_sum)
}
```


# Data selection (preparing dataset for archiving & sharing)
```{r data loading}

# Load raw data
df0.raw <- read_excel("Structural complexity_Fragment survival_2022-08.xlsx")

# Convert to long data frame
df1.clean <- as.data.frame(long_panel(df0.raw, prefix = "_", begin = 0, end = 1, label_location = "end"))
df1.clean <- select(df1.clean, -c("id", "Experiment"))
df1.clean <- df1.clean %>% rename(Time = wave)
df1.clean <- df1.clean %>% rename(Cause.death = Comments)

# Fill NAs with appropriate values
df1.clean$Cause[is.na(df1.clean$Cause)] <- "Alive"
df1.clean$Cause.death[is.na(df1.clean$Cause.death)] <- ""

# Remove fragments that were not present at the start measurement
df1.clean <- df1.clean[df1.clean$Genus != "NA", ]    

# Set variables right
df1.clean$Patch <- as.factor(df1.clean$Patch)
df1.clean$Structure <- as.factor(df1.clean$Structure)
df1.clean$Species <- as.factor(paste(df1.clean$Genus, df1.clean$Species, sep = " "))
df1.clean$Size <- factor(df1.clean$Size, ordered = TRUE, levels = c("Small", "Medium", "Large"))
df1.clean <- df1.clean %>% add_column(Survival = ifelse(df1.clean$Condition > 0, 1, 0), .after = "Condition" )
df1.clean$Treatment <- as.factor(ifelse(grepl("BRU", df1.clean$Patch), "BRU", 
                       ifelse(grepl("CAKE", df1.clean$Patch), "Cake",
                       ifelse(grepl("CAGE", df1.clean$Patch), "Cage",       
                       ifelse(grepl("COMP", df1.clean$Patch), "Compound",
                       ifelse(grepl("\\(", df1.clean$Patch), "Reference (+)", "Reference (-)"))))))
df1.clean$Cause.death <- as.factor(df1.clean$Cause.death)

```

# Data cleaning
```{r cleaning}

# Select end date only
df2.surv <- df1.clean[df1.clean$Time == 1, ]

# All structures (for correlation analysis)
df3.Structure_cor <- data_summary(df2.surv, varname = "Survival", groupnames = c("Treatment" ,"Patch", "Structure", "Number"))
df3.Structure_cor <- select(df3.Structure_cor, -c("sd", "sum", "se"))
write_xlsx(df3.Structure_cor, "Correlation data/Structural complexity_Correlations_Fragments.xlsx")

# Disks only per Treatment
df2.surv.d <- df2.surv[df2.surv$Structure == "DISK", ]
# Select only Acropora, because Pocillopora and Porites mostly died due to bleaching (not relevant for the Disks)
df2.surv.d <- df2.surv.d[df2.surv.d$Genus == "Acropora", ]
df3.Patch.d <- data_summary(df2.surv.d, varname = "Survival", groupnames = c("Treatment", "Patch", "Genus"))
df3.Treatment.d <- data_summary(df2.surv.d, varname = "Survival", groupnames = c("Treatment", "Genus"))
df3.Treatment.d <- select(df3.Treatment.d, -c("sd", "sum"))

# Deselect disks (ie focus from here onwards on ARs only)
df2.surv.nd <- df2.surv[df2.surv$Structure != "DISK", ]

# Overall survival
Total.fragments.nd <- as.numeric(nrow(df2.surv.nd))
Overall.survival.nd <- sum(df2.surv.nd$Survival)/ Total.fragments.nd * 100
Overall.condition.nd <- mean(df2.surv.nd$Condition)

# Survival per Structure type
df3.Structure  <- data_summary(df2.surv.nd, varname = "Survival", groupnames = c("Treatment" ,"Patch", "Structure", "Number"))
## Average over individual structures (assuming roughly equal fragments within each AR type)
df3.Structure <- data_summary(df3.Structure, varname = "Survival", groupnames = c("Treatment" ,"Patch", "Structure"))
df3.Structure.avg <- data_summary(df3.Structure, varname = "Survival", groupnames = c("Structure"))

# Survival per Patch (not averaged per Structure first, so relative size differences of AR types are taken into account)
df3.Patch <- data_summary(df2.surv.nd, varname = "Survival", groupnames = c("Treatment" ,"Patch"))

# Survival per Treatment (averaged per Patch, assuming each patch had roughly equal number of start fragments)
df3.Treatment <- data_summary(df3.Patch, varname = "Survival", groupnames = c("Treatment"))
df3.Treatment <- select(df3.Treatment, -c("sd", "sum"))

# Survival by Genus x Structure
df2.surv.nd$Genus[df2.surv.nd$Genus == "Isopora"] <- "Acropora"
df3.StructurexGenus <- data_summary(df2.surv.nd, varname = "Survival", groupnames = c("Structure", "Genus"))

# Survival by Size x Treatment
df3.SizexTreatment <- data_summary(df2.surv.nd, varname = "Survival", groupnames = c("Size", "Structure"))

# Cause of death
## Assuming all missing fragments died, then got lost
df3.death <- df2.surv.nd[df2.surv.nd$Survival == 0, ]
df3.death$Dead <- 1
Total.fragments.nd.dead <- as.numeric(nrow(df3.death))
# Overall
df3.Dead.Overall <- data_summary(df3.death, varname = "Dead", groupnames = c("Cause.death"))
df3.Dead.Overall$Pct <- df3.Dead.Overall$sum/ Total.fragments.nd.dead * 100
df3.Dead.Overall <- select(df3.Dead.Overall, c("Cause.death", "n", "Pct"))
# Cause x Treatment
df3.Dead.byTreatment <- data_summary(df3.death, varname = "Dead", groupnames = c("Treatment" ,"Cause.death"))
df3.Dead.byTreatment$Pct <- df3.Dead.byTreatment$sum/ Total.fragments.nd.dead * 100
df3.Dead.byTreatment <- select(df3.Dead.byTreatment, c("Treatment" ,"Cause.death", "n", "Pct"))
df3.Dead.byTreatment$Cause.death <- factor(df3.Dead.byTreatment$Cause.death, ordered = TRUE, levels = c("Predation cots", "Predation snail", "Coral", "Soft coral", "Sponge", "Tunicate", "Turtle", "Fishing", "Toppled", "Bleaching", "Unknown"))
levels(df3.Dead.byTreatment$Cause.death) <- c("COTS", "Snails", "Hard coral", "Soft coral", "Sponge", "Tunicate", "Turtle", "Fishing", "Toppled", "Bleaching", "Unknown")
# Cause x Genus
df3.Dead.byGenus <- data_summary(df3.death, varname = "Dead", groupnames = c("Genus" ,"Cause.death"))
df3.Dead.byGenus$Pct <- df3.Dead.byGenus$sum/ Total.fragments.nd.dead * 100
df3.Dead.byGenus <- select(df3.Dead.byGenus, c("Genus" ,"Cause.death", "n", "Pct"))
df3.Dead.byGenus$Cause.death <- factor(df3.Dead.byGenus$Cause.death, ordered = TRUE, levels = c("Predation cots", "Predation snail", "Coral", "Soft coral", "Sponge", "Tunicate", "Turtle", "Fishing", "Toppled", "Bleaching", "Unknown"))
levels(df3.Dead.byGenus$Cause.death) <- c("COTS", "Snails", "Hard coral", "Soft coral", "Sponge", "Tunicate", "Turtle", "Fishing", "Toppled", "Bleaching", "Unknown")

```

# Data exploration
```{r data exploration}

# Data per Patch normal, Data per structure not
hist(df3.Structure$Survival) # Per structure (averaged per patch)
hist(df3.Patch$Survival) # Per patch (structures pooled)
```

# Models
```{r models}

# ---- TREATMENT DISKS ONLY ----
## Using Patch averages instead of individual Structures, because of distribution
### Linear model
### Beta regression (because fraction)
### Transformation needed, because of exact 0s and 1s
df3.Patch.d <- df3.Patch.d %>% 
  mutate(Survival = (Survival * (length(Survival) - 1) + 0.5) / length(Survival))

bm.TD1 <- betareg(Survival ~ Treatment, data = df3.Patch.d)

### Variable precision
bm.TD1b <- betareg(Survival ~ Treatment | Treatment, data = df3.Patch.d)

car::Anova(bm.TD1b) 

# ---- TREATMENT ----
## Using Patch averages instead of individual Structures, because of distribution
### Linear model
### Beta regression (because fraction)
### No transformation needed, because no exact 0s or 1s
bm.T1 <- betareg(Survival ~ Treatment, data = df3.Patch)

### Variable precision
bm.T1b <- betareg(Survival ~ Treatment | Treatment, data = df3.Patch)

car::Anova(bm.T1b) 

# ---- STRUCTURE ----
## Using Patch averages instead of individual Structures, because of distribution
### Beta regression (because fraction)
### No transformation needed, because no exact 0s or 1s
bm.S1 <- betareg(Survival ~ Structure, data = df3.Structure)

### Variable precision
bm.S1b <- betareg(Survival ~ Structure | Treatment, data = df3.Structure)

car::Anova(bm.S1b) 

```


```{r AVG survival: model validation}

# TREATMENT BY DISK
mod <- bm.TD1b # set model to be validated
op <- par(mfrow = c(2, 4), mar = c(5, 4, 1, 2)) # set layout of figure frame
plot(resid(mod, type = "pearson") ~ fitted(mod)) # fitted vs residuals
abline(0,0)
hist(resid(mod, type = "pearson"), main = "") # histogram residuals
qqnorm(resid(mod, type = "pearson")) # QQplot residuals
plot(df3.Patch.d$Treatment, resid(mod, type = "pearson")) # residuals split over Treatment
abline(0,0)
plot(fitted(mod) ~ df3.Patch.d$Survival) # response data vs fitted
par(op)

# TREATMENT
mod <- bm.T1b # set model to be validated
op <- par(mfrow = c(2, 4), mar = c(5, 4, 1, 2)) # set layout of figure frame
plot(resid(mod, type = "pearson") ~ fitted(mod)) # fitted vs residuals
abline(0,0)
hist(resid(mod, type = "pearson"), main = "") # histogram residuals
qqnorm(resid(mod, type = "pearson")) # QQplot residuals
plot(df3.Patch$Treatment, resid(mod, type = "pearson")) # residuals split over Treatment
abline(0,0)
plot(fitted(mod) ~ df3.Patch$Survival) # response data vs fitted
par(op)

# STRUCTURE
mod <- bm.S1b # set model to be validated
op <- par(mfrow = c(2, 4), mar = c(5, 4, 1, 2)) # set layout of figure frame
plot(resid(mod, type = "pearson") ~ fitted(mod)) # fitted vs residuals
abline(0,0)
hist(resid(mod, type = "pearson"), main = "") # histogram residuals
qqnorm(resid(mod, type = "pearson")) # QQplot residuals
plot(df3.Structure$Structure, resid(mod, type = "pearson")) # residuals split over Treatment
abline(0,0)
plot(fitted(mod) ~ df3.Structure$Survival) # response data vs fitted
par(op)


```


# Post hoc
```{r post hoc}
# TREATMENT BY DISK
## No post hoc because no significant main effect

# TREATMENT
hsd.Treatment <- emmeans(bm.T1b, specs = pairwise ~ Treatment, adjust = "tukey", type = "response")

# STRUCTURE
hsd.Structure <- emmeans(bm.S1b, specs = pairwise ~ Structure, adjust = "tukey", type = "response")

```


# Plot
```{r plot}

# ---- TREATMENT BY DISK ----

# Plot
ggplot(df3.Treatment.d, aes(x = Treatment, y = Survival))+
  geom_bar(stat = "identity", position = position_dodge())+ 
  labs(y = "Survival on disk (F)", x = "Treatment")+
  scale_y_continuous(limits = c (0, 1), expand = c(0,0))+
  geom_errorbar(aes(ymin=Survival-(1*se), ymax=Survival+(1*se)), width=.2, position=position_dodge(.9))+
  scale_x_discrete(expand = c(0, 0.7))+
  theme_economist()+scale_colour_economist()+
  theme(
    panel.margin.y = unit(0, "cm"),
    strip.text.x = element_text(size = 14, face = "bold", vjust = 2, margin = margin(0.2, 0, 0.1, 0, "cm")),
    strip.background = element_blank(),
    axis.title.x = element_text(color="black", vjust=-2, size = 14),
    axis.text.x = element_text(angle = 0, size=12, face = "bold", vjust=0.5),
    axis.title.y = element_text(color="black" , vjust=4, size = 14),
    axis.text.y=element_text(size=12, face = "bold", vjust=0.4),
    plot.margin = margin(t = 10, r = 40,  b = 25,  l = 20),
    panel.background = element_rect(fill = "#FCFCFC"),
    plot.background = element_rect(fill = "#FFFFFF"),
    panel.grid.major = element_line(colour = "#797979", size = 0.3),
    axis.ticks = element_blank()
    )
ggsave("Fragment survival_Treatment on Disk.tiff", width = 23, height = 14, units = "cm", dpi=1200, compression = "lzw")


# ---- TREATMENT ----
# Post hoc letters
sigletters.T <- multcomp::cld(hsd.Treatment$emmeans, alpha = 0.05, Letters = letters, reversed = FALSE) # get CLD

# Make order match with summary dataframe
sigletters.T <- sigletters.T[order(sigletters.T$Treatment),]
sigletters.T <- sigletters.T %>% dplyr::mutate(.group = str_squish(.group)) # remove white spaces

# Merge sig.letter dataframe into the summary dataframe
df3.Treatment <- df3.Treatment[order(df3.Treatment$Treatment),]
df3.Treatment.fig <- cbind(df3.Treatment, siglet.loc = sigletters.T$.group)

# Plot
ggplot(df3.Treatment.fig, aes(x = Treatment, y = Survival))+
  geom_bar(stat = "identity", position = position_dodge())+ 
  labs(y = "Survival (F)", x = "Treatment")+
  scale_y_continuous(limits = c (0, 1), expand = c(0,0))+
  geom_errorbar(aes(ymin=Survival-(1*se), ymax=Survival+(1*se)), width=.2, position=position_dodge(.9))+
  geom_text(data = df3.Treatment.fig, aes(x=Treatment, y = Survival + (1*se), label = siglet.loc), 
            vjust= -0.8, hjust = 0.5, size = 5, fontface = "bold", position=position_dodge(.9))+
  scale_x_discrete(expand = c(0, 0.7))+
  theme_economist()+scale_colour_economist()+
  theme(
    panel.margin.y = unit(0, "cm"),
    strip.text.x = element_text(size = 14, face = "bold", vjust = 2, margin = margin(0.2, 0, 0.1, 0, "cm")),
    strip.background = element_blank(),
    axis.title.x = element_text(color="black", vjust=-2, size = 14),
    axis.text.x = element_text(angle = 0, size=12, face = "bold", vjust=0.5),
    axis.title.y = element_text(color="black" , vjust=4, size = 14),
    axis.text.y=element_text(size=12, face = "bold", vjust=0.4),
    plot.margin = margin(t = 10, r = 40,  b = 25,  l = 20),
    panel.background = element_rect(fill = "#FCFCFC"),
    plot.background = element_rect(fill = "#FFFFFF"),
    panel.grid.major = element_line(colour = "#797979", size = 0.3),
    axis.ticks = element_blank()
    )
ggsave("Fragment survival_Treatment.tiff", width = 23, height = 14, units = "cm", dpi=1200, compression = "lzw")

# ---- STRUCTURE X SIZE ----

# Plot
ggplot(df3.SizexTreatment, aes(fill = Size, x = Structure, y = Survival))+
  geom_bar(stat = "identity", position = position_dodge())+ 
  labs(y = "Survival (F)", x = "Structure")+
  scale_y_continuous(limits = c (0, 1), expand = c(0,0))+
  geom_errorbar(aes(ymin=Survival-(1*se), ymax=Survival+(1*se)), width=.2, position=position_dodge(.9))+
  #geom_text(data = df3.Treatment.fig, aes(x=Treatment, y = Survival + (1*se), label = siglet.loc), 
   #         vjust= -0.8, hjust = 0.5, size = 5, fontface = "bold", position=position_dodge(.9))+
  scale_x_discrete(expand = c(0, 0.7))+
  theme_economist()+scale_colour_economist()+
  theme(
    panel.margin.y = unit(0, "cm"),
    strip.text.x = element_text(size = 14, face = "bold", vjust = 2, margin = margin(0.2, 0, 0.1, 0, "cm")),
    strip.background = element_blank(),
    axis.title.x = element_text(color="black", vjust=-2, size = 14),
    axis.text.x = element_text(angle = 0, size=12, face = "bold", vjust=0.5),
    axis.title.y = element_text(color="black" , vjust=4, size = 14),
    axis.text.y=element_text(size=12, face = "bold", vjust=0.4),
    plot.margin = margin(t = 10, r = 40,  b = 25,  l = 20),
    panel.background = element_rect(fill = "#FCFCFC"),
    plot.background = element_rect(fill = "#FFFFFF"),
    panel.grid.major = element_line(colour = "#797979", size = 0.3),
    axis.ticks = element_blank()
    )
ggsave("Fragment survival_Structure x Size.tiff", width = 23, height = 14, units = "cm", dpi=1200, compression = "lzw")

# ---- STRUCTURE X GENUS ----

# Plot
ggplot(df3.StructurexGenus, aes(fill = Structure, x = Genus, y = Survival))+
  geom_bar(stat = "identity", position = position_dodge())+ 
  labs(y = "Survival (F)", x = "Structure")+
  scale_y_continuous(limits = c (0, 1), expand = c(0,0))+
  geom_errorbar(aes(ymin=Survival-(1*se), ymax=Survival+(1*se)), width=.2, position=position_dodge(.9))+
  #geom_text(data = df3.Treatment.fig, aes(x=Treatment, y = Survival + (1*se), label = siglet.loc), 
   #         vjust= -0.8, hjust = 0.5, size = 5, fontface = "bold", position=position_dodge(.9))+
  scale_x_discrete(expand = c(0, 0.7))+
  theme_economist()+scale_colour_economist()+
  theme(
    panel.margin.y = unit(0, "cm"),
    strip.text.x = element_text(size = 14, face = "bold", vjust = 2, margin = margin(0.2, 0, 0.1, 0, "cm")),
    strip.background = element_blank(),
    axis.title.x = element_text(color="black", vjust=-2, size = 14),
    axis.text.x = element_text(angle = 0, size=12, face = "bold", vjust=0.5),
    axis.title.y = element_text(color="black" , vjust=4, size = 14),
    axis.text.y=element_text(size=12, face = "bold", vjust=0.4),
    plot.margin = margin(t = 10, r = 40,  b = 25,  l = 20),
    panel.background = element_rect(fill = "#FCFCFC"),
    plot.background = element_rect(fill = "#FFFFFF"),
    panel.grid.major = element_line(colour = "#797979", size = 0.3),
    axis.ticks = element_blank()
    )
ggsave("Fragment survival_Structure x Genus.tiff", width = 23, height = 14, units = "cm", dpi=1200, compression = "lzw")

# ---- STRUCTURE ----
# Post hoc letters
sigletters.S <- multcomp::cld(hsd.Structure$emmeans, alpha = 0.05, Letters = letters, reversed = FALSE) # get CLD

# Make order match with summary dataframe
sigletters.S <- sigletters.S[order(sigletters.S$Structure),]
sigletters.S <- sigletters.S %>% dplyr::mutate(.group = str_squish(.group)) # remove white spaces

# Merge sig.letter dataframe into the summary dataframe
df3.Structure.avg <- df3.Structure.avg[order(df3.Structure.avg$Structure),]
df3.Structure.fig <- cbind(df3.Structure.avg, siglet.loc = sigletters.S$.group)

# Plot
ggplot(df3.Structure.fig, aes(x = Structure, y = Survival))+
  geom_bar(stat = "identity", position = position_dodge())+ 
  labs(y = "Survival (F)", x = "Structure")+
  scale_y_continuous(limits = c (0, 1), expand = c(0,0))+
  geom_errorbar(aes(ymin=Survival-(1*se), ymax=Survival+(1*se)), width=.2, position=position_dodge(.9))+
  geom_text(data = df3.Structure.fig, aes(x=Structure, y = Survival + (1*se), label = siglet.loc), 
            vjust= -0.8, hjust = 0.5, size = 5, fontface = "bold", position=position_dodge(.9))+
  scale_x_discrete(expand = c(0, 0.7))+
  theme_economist()+scale_colour_economist()+
  theme(
    panel.margin.y = unit(0, "cm"),
    strip.text.x = element_text(size = 14, face = "bold", vjust = 2, margin = margin(0.2, 0, 0.1, 0, "cm")),
    strip.background = element_blank(),
    axis.title.x = element_text(color="black", vjust=-2, size = 14),
    axis.text.x = element_text(angle = 0, size=12, face = "bold", vjust=0.5),
    axis.title.y = element_text(color="black" , vjust=4, size = 14),
    axis.text.y=element_text(size=12, face = "bold", vjust=0.4),
    plot.margin = margin(t = 10, r = 40,  b = 25,  l = 20),
    panel.background = element_rect(fill = "#FCFCFC"),
    plot.background = element_rect(fill = "#FFFFFF"),
    panel.grid.major = element_line(colour = "#797979", size = 0.3),
    axis.ticks = element_blank()
    )

# ---- DEATHS ----

## DEATH x TREATMENT
## TODO: MAYBE BETTER: DEATH x STRUCTURE (as compound is just a mix)
ggplot(df3.Dead.byTreatment, aes(fill=Cause.death, y=n, x=Treatment)) + 
    geom_bar(position="fill", stat="identity")+
    scale_fill_manual(values = c("#A93226", "#EB984E", "#82E0AA", "#73C6B6", "#85C1E9", "#D2B4DE", "#5D6D7E",
                                 "#99A3A4", "#D5D8DC", "#FEF9E7", "#17202A"))+
    labs(y = "Deaths (F)", x = "Treatment", fill = "Cause")+
    scale_y_continuous(expand = c(0,0))+
    theme_economist()+
    theme(
      axis.title.x = element_text(color="black", vjust=-2, size = 14),
      axis.text.x=element_text(size=12, face = "bold.italic", vjust=0.5, angle = -35, hjust=0),
      axis.title.y = element_text(color="black" , vjust=4, size = 14),
      axis.text.y=element_text(size=12, face = "bold", vjust=0.5),
      plot.margin = unit(c(0.5,3.5,0.5,0.5), "cm"),
      panel.background = element_rect(fill = "#FCFCFC"),
      plot.background = element_rect(fill = "#FFFFFF"),
      panel.grid.major = element_line(colour = "#797979", size = 0.3),
      axis.ticks.length = unit(0.15, "cm")
      )
ggsave("Fragment deaths_Treatment.tiff", width = 23, height = 12, units = "cm", dpi=1200, compression = "lzw")

## DEATH x GENUS
ggplot(df3.Dead.byGenus, aes(fill=Cause.death, y=n, x=Genus)) + 
    geom_bar(position="fill", stat="identity")+
    scale_fill_manual(values = c("#A93226", "#EB984E", "#82E0AA", "#73C6B6", "#85C1E9", "#D2B4DE", "#5D6D7E",
                                 "#99A3A4", "#D5D8DC", "#FEF9E7", "#17202A"))+
    labs(y = "Deaths (F)", x = "Genus", fill = "Cause")+
    scale_y_continuous(expand = c(0,0))+
    theme_economist()+
    theme(
      axis.title.x = element_text(color="black", vjust=-2, size = 14),
      axis.text.x=element_text(size=12, face = "bold.italic", vjust=0.5, angle = -35, hjust=0),
      axis.title.y = element_text(color="black" , vjust=4, size = 14),
      axis.text.y=element_text(size=12, face = "bold", vjust=0.5),
      plot.margin = unit(c(0.5,3.5,0.5,0.5), "cm"),
      panel.background = element_rect(fill = "#FCFCFC"),
      plot.background = element_rect(fill = "#FFFFFF"),
      panel.grid.major = element_line(colour = "#797979", size = 0.3),
      axis.ticks.length = unit(0.15, "cm")
      )
ggsave("Fragment deaths_Genus.tiff", width = 23, height = 12, units = "cm", dpi=1200, compression = "lzw")

```





